\documentclass[fleqn]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{mathexam}
\usepackage{multicol}
\usepackage{verbatim}

\ExamClass{CSCE 240}
\ExamName{Homework 6}
\ExamHead{Due: 16 June 2021}

\let
\ds
\displaystyle

\begin{document}
\ExamInstrBox {
  You must submit a zipped, \textbf{and only zipped}, archive of your homework
  directory, hw6. The directory must contain, at a minimum, the files
  \texttt{hw6/src/grade.cc}, \texttt{hw6/inc/grade.h},
  \texttt{hw6/src/rational.cc} and \texttt{hw6/inc/rational.h}. Name the
  archive submission file hw6.zip \\
  \\
  I will use my own makefile to compile and link to your
  \texttt{hw6/src/grade.cc}, \texttt{hw6/inc/grade.h},
  \texttt{hw6/src/rational.cc} and \texttt{hw6/inc/rational.h} files. You must
  submit, at least, these four files.
}
%
\subsection*{Introduction}
In this assignment, you will update your Grade class again, this time eschewing
inheritance to use a Template. I require your Rational class to test your Grade
class and list the necessary methods below. In this version, Rational is passed
as a template to Grade and will likely require additional overloaded operators
to implement the methods in Grade. \\
\\
%
Read the provided header file documentation for instructions on how the
methods should work.
%
\subsection*{Points}
\begin{multicols*}{2}
  \subsubsection*{Correctness}
    \begin{enumerate}
      \item \texttt{Grade::Grade}: 1.05 points
      \item \texttt{Grade::ToLetter}: 1.75 points
      \item \texttt{Grade::CalcAverage}: 1.5 points
      \item \texttt{operator<<(Rational)}: 1.75 points
      \item \texttt{Rational::operator==()}: 1.45 points
    \end{enumerate}
    Total: 7.5 Points Possible
  \columnbreak
  \subsubsection*{Base Submission}
    \begin{itemize}
      \item compilation of each test (ten tests above): 0.1 points each
      \item \texttt{hw5/src/grade.cc} style: 0.5 points
      \item \texttt{hw5/inc/grade.h} style: 0.5 points
      \item \texttt{hw5/src/rational.cc} style: 0.5 points
      \item \texttt{hw5/inc/rational.h} style: 0.5 points
    \end{itemize}
    Total: 2.5 Points Possible
\end{multicols*}
%
\subsubsection*{Notes}
I have provided you basic test apps which you can use to ensure that your code
is, at least partially, correct. I would suggest a more rigorous testing scheme
to ensure that you test overloaded operators you require, but that I do not
request. \\
%
\\
Late assignments will be accepted without penalty until 11:59 PM 20 June. No
assignment will be accepted after this time. The assignment will be removed
from Blackboard at that time. Any submission will be graded and if it is
greater than the student's current Homework average, will be kept. Those below
the average will be exempted. \\
\\
Though this assignment cannot hurt you, I \textbf{strongly} recommend you work on it and attempt a complete submission. There will be problems on the final exam focused entirely on the topics in this assignment.
\end{document}

